Untitled

### 2022-12-21 Figuring_Q3.Rmd
Changing Q3 part b

---
title: "Untitled"
output: html_document
date: "2022-12-14"
---
```{r}
# Part b
calcDirichletPDF <- function(x,a){

>>>>

---
title: "Untitled"
output: html_document
date: "2022-12-14"
---

### Part b ###

calcDirichletPDF <- function(x,a){

calcDirichletPDF(c(0.2,0.3,0.5),c(3,4,5))

calcDirichletPDF.2 <- function(x,a){
  #Calculating density of x under Dirichlet distribution with parameters specified by a
  log.density <- lgamma(sum(a))-sum(lgamma(a))+sum((a-1)*log(x))
  return(c(log.density))
}

calcDirichletPDF.2(c(0.2,0.3,0.5),c(3,4,5))

### Part c ###

simDirichletRV <- function(a){
  #Drawing from gamma distribution
  U <- rgamma(a,1)
  #Computing V a vector drawn from Dirichlet distribution with parameters specified by a
  V <- U/sum(U)

### Part d ###

  }
  #Removing burn in samples
  return(PT[,,(burnin+1):(n+burnin+1)])
}

PT.sample <- q3.mcmc(rep("c",1000),initStateProbs,initPT,burnin,n)

PT.expected <- matrix(c(mean(PT.sample[1,1,]),mean(PT.sample[1,2,]),mean(PT.sample[1,3,]),
                        mean(PT.sample[2,1,]),mean(PT.sample[2,2,]),mean(PT.sample[2,3,]),
                        mean(PT.sample[3,1,]),mean(PT.sample[3,2,]),mean(PT.sample[3,3,])),ncol=3,nrow=3,byrow = T)
round(PT.expected,3)

plot(PT.sample[2,2,],type="l")

acf(PT.sample[2,2,])
#autocorrelation goes to nothing very quickly :)

hist(PT.sample,breaks=50)
#Looks like distrbution so maybe isn't broken :)
```

```{r}
# Part b
calcDirichletPDF <- function(x,a){
